\vspace{30mm} {\Large\bf RISC-V Duo-PLIC for the Advancced Interrupt Architecture} \\ {\large Document Version \DuoPLICRev}

### 2023-05-09 doc/src/CSRs.tex
Change widths of *iselect and *ireg CSRs to be always current XLEN
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|c|c|l|l|}
\hline
Number & Privilege & Width & Name & Description \\
\hline
\hline
\multicolumn{5}{|c|}{Machine-Level Window to Indirectly Accessed Registers} \\
\hline
\z{0x350} & MRW & MXLEN & \z{miselect} & Machine indirect register select \\
\z{0x351} & MRW & MXLEN & \z{mireg}    & Machine indirect register alias \\
\hline
\multicolumn{5}{|c|}{Machine-Level Interrupts} \\
\hline
\z{0x304} & MRW & 64    & \z{mie}    & Machine interrupt-enable bits \\
\z{0x344} & MRW & 64    & \z{mip}    & Machine interrupt-pending bits \\
\z{0x35C} & MRW & MXLEN & \z{mtopei}
                              & Machine top external interrupt (only with an \\
          &     &       &            & \quad IMSIC) \\
\z{0xFB0} & MRO & MXLEN & \z{mtopi}  & Machine top interrupt \\
\hline
\multicolumn{5}{|c|}{Delegated and Virtual Interrupts for Supervisor Level} \\
\hline
\z{0x303} & MRW & 64 & \z{mideleg} & Machine interrupt delegation \\
\z{0x308} & MRW & 64 & \z{mvien}   & Machine virtual interrupt enables \\
\z{0x309} & MRW & 64 & \z{mvip}    & Machine virtual interrupt-pending bits \\
\hline
\multicolumn{5}{|c|}{Machine-Level High-Half CSRs (RV32 only)} \\
\hline
\z{0x313} & MRW & 32 & \z{midelegh}
                        & Upper 32 bits of of \z{mideleg} (only with S-mode) \\
\z{0x314} & MRW & 32 & \z{mieh} & Upper 32 bits of \z{mie} \\
\z{0x318} & MRW & 32 & \z{mvienh}
                             & Upper 32 bits of \z{mvien} (only with S-mode) \\
\z{0x319} & MRW & 32 & \z{mviph}
                              & Upper 32 bits of \z{mvip} (only with S-mode) \\
\z{0x354} & MRW & 32 & \z{miph} & Upper 32 bits of \z{mip} \\
\hline
\end{tabular}
\end{center}
\caption{%
Machine-level CSRs added or widened by the Advanced Interrupt Architecture.%
}
\label{tab:CSRs-M}
\end{table*}

@@

Values of \z{miselect} with the most-significant bit set
(bit $\mbox{MXLEN - 1} = \mbox{1}$) are designated for custom use,
presumably for accessing custom registers through \z{mireg}.
If MXLEN is changed, the most-significant bit of \z{miselect} moves to
the new position, retaining its value from before.
An implementation is not required to support any custom values for
\z{miselect}.

@@

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|c|c|l|l|}
\hline
Number & Privilege & Width & Name      & Description \\
\hline
\hline
\multicolumn{5}{|c|}{%
  Supervisor-Level Window to Indirectly Accessed Registers} \\
\hline
\z{0x150} & SRW & SXLEN & \z{siselect} & Supervisor indirect register select \\
\z{0x151} & SRW & SXLEN & \z{sireg}    & Supervisor indirect register alias \\
\hline
\multicolumn{5}{|c|}{Supervisor-Level Interrupts} \\
\hline
\z{0x104} & SRW & 64    & \z{sie}      & Supervisor interrupt-enable bits \\
\z{0x144} & SRW & 64    & \z{sip}      & Supervisor interrupt-pending bits \\
\z{0x15C} & SRW & SXLEN & \z{stopei}
                                   & Supervisor top external interrupt (only \\
          &     &       &          & \quad with an IMSIC) \\
\z{0xDB0} & SRO & SXLEN & \z{stopi}    & Supervisor top interrupt \\
\hline
\multicolumn{5}{|c|}{Supervisor-Level High-Half CSRs (RV32 only)} \\
\hline
\z{0x114} & SRW & 32    & \z{sieh}     & Upper 32 bits of \z{sie} \\
\z{0x154} & SRW & 32    & \z{siph}     & Upper 32 bits of \z{sip} \\
\hline
\end{tabular}
\end{center}
\caption{%
Supervisor-level CSRs added or widened by the Advanced Interrupt Architecture.%
}
\label{tab:CSRs-S}
\end{table*}

@@

Like \z{miselect}, values of \z{siselect} with the most-significant bit
set (bit $\mbox{SXLEN - 1} = \mbox{1}$) are designated for custom use.
If SXLEN is changed, the most-significant bit of \z{siselect} moves to
the new position, retaining its value from before.
An implementation is not required to support any custom values for
\z{siselect}.

@@

@@

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|c|c|l|l|}
\hline
Number & Privilege & Width & Name & Description \\
\hline
\hline
\multicolumn{5}{|c|}{%
  Delegated and Virtual Interrupts, Interrupt Priorities, for VS Level%
} \\
\hline
\z{0x603} & HRW & 64     & \z{hideleg} & Hypervisor interrupt delegation \\
\z{0x608} & HRW & 64     & \z{hvien}  & Hypervisor virtual interrupt enables \\
\z{0x609} & HRW & HSXLEN & \z{hvictl} & Hypervisor virtual interrupt control \\
\z{0x645} & HRW & 64     & \z{hvip}
                                 & Hypervisor virtual interrupt-pending bits \\
\z{0x646} & HRW & 64     & \z{hviprio1}
                                 & Hypervisor VS-level interrupt priorities \\
\z{0x647} & HRW & 64     & \z{hviprio2}
                                 & Hypervisor VS-level interrupt priorities \\
\hline
\multicolumn{5}{|c|}{VS-Level Window to Indirectly Accessed Registers} \\
\hline
\z{0x250} & HRW & VSXLEN & \z{vsiselect}
                               & Virtual supervisor indirect register select \\
\z{0x251} & HRW & VSXLEN & \z{vsireg}
                               & Virtual supervisor indirect register alias \\
\hline
\multicolumn{5}{|c|}{VS-Level Interrupts} \\
\hline
\z{0x204} & HRW & 64     & \z{vsie}
                                 & Virtual supervisor interrupt-enable bits \\
\z{0x244} & HRW & 64     & \z{vsip}
                                 & Virtual supervisor interrupt-pending bits \\
\z{0x25C} & HRW & VSXLEN & \z{vstopei}
                           & Virtual supervisor top external interrupt (only \\
          &     &        & & \quad with an IMSIC) \\
\z{0xEB0} & HRO & VSXLEN & \z{vstopi} & Virtual supervisor top interrupt \\
\hline
\multicolumn{5}{|c|}{Hypervisor and VS-Level High-Half CSRs (RV32 only)} \\
\hline
\z{0x613} & HRW & 32     & \z{hidelegh}  & Upper 32 bits of \z{hideleg} \\
\z{0x618} & HRW & 32     & \z{hvienh}    & Upper 32 bits of \z{hvien} \\
\z{0x655} & HRW & 32     & \z{hviph}     & Upper 32 bits of \z{hvip} \\
\z{0x656} & HRW & 32     & \z{hviprio1h} & Upper 32 bits of \z{hviprio1} \\
\z{0x657} & HRW & 32     & \z{hviprio2h} & Upper 32 bits of \z{hviprio2} \\
\z{0x214} & HRW & 32     & \z{vsieh}     & Upper 32 bits of \z{vsie} \\
\z{0x254} & HRW & 32     & \z{vsiph}     & Upper 32 bits of \z{vsip} \\
\hline
\end{tabular}
\end{center}
\caption{%
Hypervisor and VS CSRs added or widened
by the Advanced Interrupt Architecture.
(Parameter HSXLEN is just another name for
SXLEN for hypervisor-extended \mbox{S-mode}).%
}
\label{tab:CSRs-hypervisor}
\end{table*}

@@

CSR \z{vsiselect} is required to support at least a \mbox{9-bit} range
of 0 to \z{0x1FF}, whether or not an IMSIC is implemented.
As with \z{siselect}, values of \z{vsiselect} with the most-significant
bit set (bit $\mbox{VSXLEN - 1} = \mbox{1}$) are designated for custom
use.
If VSXLEN is changed, the most-significant bit of \z{vsiselect} moves
to the new position, retaining its value from before.

>>>>

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|c|c|l|l|}
\hline
Number & Privilege & Width & Name & Description \\
\hline
\hline
\multicolumn{5}{|c|}{Machine-Level Window to Indirectly Accessed Registers} \\
\hline
\z{0x350} & MRW & XLEN  & \z{miselect} & Machine indirect register select \\
\z{0x351} & MRW & XLEN  & \z{mireg}    & Machine indirect register alias \\
\hline
\multicolumn{5}{|c|}{Machine-Level Interrupts} \\
\hline
\z{0x304} & MRW & 64    & \z{mie}    & Machine interrupt-enable bits \\
\z{0x344} & MRW & 64    & \z{mip}    & Machine interrupt-pending bits \\
\z{0x35C} & MRW & MXLEN & \z{mtopei}
                              & Machine top external interrupt (only with an \\
          &     &       &            & \quad IMSIC) \\
\z{0xFB0} & MRO & MXLEN & \z{mtopi}  & Machine top interrupt \\
\hline
\multicolumn{5}{|c|}{Delegated and Virtual Interrupts for Supervisor Level} \\
\hline
\z{0x303} & MRW & 64 & \z{mideleg} & Machine interrupt delegation \\
\z{0x308} & MRW & 64 & \z{mvien}   & Machine virtual interrupt enables \\
\z{0x309} & MRW & 64 & \z{mvip}    & Machine virtual interrupt-pending bits \\
\hline
\multicolumn{5}{|c|}{Machine-Level High-Half CSRs (RV32 only)} \\
\hline
\z{0x313} & MRW & 32 & \z{midelegh}
                        & Upper 32 bits of of \z{mideleg} (only with S-mode) \\
\z{0x314} & MRW & 32 & \z{mieh} & Upper 32 bits of \z{mie} \\
\z{0x318} & MRW & 32 & \z{mvienh}
                             & Upper 32 bits of \z{mvien} (only with S-mode) \\
\z{0x319} & MRW & 32 & \z{mviph}
                              & Upper 32 bits of \z{mvip} (only with S-mode) \\
\z{0x354} & MRW & 32 & \z{miph} & Upper 32 bits of \z{mip} \\
\hline
\end{tabular}
\end{center}
\caption{%
Machine-level CSRs added or widened by the Advanced Interrupt Architecture.%
}
\label{tab:CSRs-M}
\end{table*}

@@

Values of \z{miselect} with the most-significant bit set
(bit $\mbox{XLEN - 1} = \mbox{1}$) are designated for custom use,
presumably for accessing custom registers through \z{mireg}.
If XLEN changes, the most-significant bit of \z{miselect} moves to
the new position, retaining its value from before.
An implementation is not required to support any custom values for
\z{miselect}.

@@

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|c|c|l|l|}
\hline
Number & Privilege & Width & Name      & Description \\
\hline
\hline
\multicolumn{5}{|c|}{%
  Supervisor-Level Window to Indirectly Accessed Registers} \\
\hline
\z{0x150} & SRW & XLEN  & \z{siselect} & Supervisor indirect register select \\
\z{0x151} & SRW & XLEN  & \z{sireg}    & Supervisor indirect register alias \\
\hline
\multicolumn{5}{|c|}{Supervisor-Level Interrupts} \\
\hline
\z{0x104} & SRW & 64    & \z{sie}      & Supervisor interrupt-enable bits \\
\z{0x144} & SRW & 64    & \z{sip}      & Supervisor interrupt-pending bits \\
\z{0x15C} & SRW & SXLEN & \z{stopei}
                                   & Supervisor top external interrupt (only \\
          &     &       &          & \quad with an IMSIC) \\
\z{0xDB0} & SRO & SXLEN & \z{stopi}    & Supervisor top interrupt \\
\hline
\multicolumn{5}{|c|}{Supervisor-Level High-Half CSRs (RV32 only)} \\
\hline
\z{0x114} & SRW & 32    & \z{sieh}     & Upper 32 bits of \z{sie} \\
\z{0x154} & SRW & 32    & \z{siph}     & Upper 32 bits of \z{sip} \\
\hline
\end{tabular}
\end{center}
\caption{%
Supervisor-level CSRs added or widened by the Advanced Interrupt Architecture.%
}
\label{tab:CSRs-S}
\end{table*}

@@

Like \z{miselect}, values of \z{siselect} with the most-significant bit
set (bit $\mbox{XLEN - 1} = \mbox{1}$) are designated for custom use.
If XLEN changes, the most-significant bit of \z{siselect} moves to
the new position, retaining its value from before.
An implementation is not required to support any custom values for
\z{siselect}.

@@

Note that the widths of \z{siselect} and \z{sireg}
are always the current XLEN rather than SXLEN\@.
Hence, for example, if MXLEN = 64 and SXLEN = 32, then these registers
are 64~bits when the current privilege mode is M (running RV64 code)
but 32~bits when the privilege mode is S (RV32 code).

@@

\begin{table*}[h!]
\begin{center}
\begin{tabular}{|c|c|c|l|l|}
\hline
Number & Privilege & Width & Name & Description \\
\hline
\hline
\multicolumn{5}{|c|}{%
  Delegated and Virtual Interrupts, Interrupt Priorities, for VS Level%
} \\
\hline
\z{0x603} & HRW & 64     & \z{hideleg} & Hypervisor interrupt delegation \\
\z{0x608} & HRW & 64     & \z{hvien}  & Hypervisor virtual interrupt enables \\
\z{0x609} & HRW & HSXLEN & \z{hvictl} & Hypervisor virtual interrupt control \\
\z{0x645} & HRW & 64     & \z{hvip}
                                 & Hypervisor virtual interrupt-pending bits \\
\z{0x646} & HRW & 64     & \z{hviprio1}
                                 & Hypervisor VS-level interrupt priorities \\
\z{0x647} & HRW & 64     & \z{hviprio2}
                                 & Hypervisor VS-level interrupt priorities \\
\hline
\multicolumn{5}{|c|}{VS-Level Window to Indirectly Accessed Registers} \\
\hline
\z{0x250} & HRW & XLEN   & \z{vsiselect}
                               & Virtual supervisor indirect register select \\
\z{0x251} & HRW & XLEN   & \z{vsireg}
                               & Virtual supervisor indirect register alias \\
\hline
\multicolumn{5}{|c|}{VS-Level Interrupts} \\
\hline
\z{0x204} & HRW & 64     & \z{vsie}
                                 & Virtual supervisor interrupt-enable bits \\
\z{0x244} & HRW & 64     & \z{vsip}
                                 & Virtual supervisor interrupt-pending bits \\
\z{0x25C} & HRW & VSXLEN & \z{vstopei}
                           & Virtual supervisor top external interrupt (only \\
          &     &        & & \quad with an IMSIC) \\
\z{0xEB0} & HRO & VSXLEN & \z{vstopi} & Virtual supervisor top interrupt \\
\hline
\multicolumn{5}{|c|}{Hypervisor and VS-Level High-Half CSRs (RV32 only)} \\
\hline
\z{0x613} & HRW & 32     & \z{hidelegh}  & Upper 32 bits of \z{hideleg} \\
\z{0x618} & HRW & 32     & \z{hvienh}    & Upper 32 bits of \z{hvien} \\
\z{0x655} & HRW & 32     & \z{hviph}     & Upper 32 bits of \z{hvip} \\
\z{0x656} & HRW & 32     & \z{hviprio1h} & Upper 32 bits of \z{hviprio1} \\
\z{0x657} & HRW & 32     & \z{hviprio2h} & Upper 32 bits of \z{hviprio2} \\
\z{0x214} & HRW & 32     & \z{vsieh}     & Upper 32 bits of \z{vsie} \\
\z{0x254} & HRW & 32     & \z{vsiph}     & Upper 32 bits of \z{vsip} \\
\hline
\end{tabular}
\end{center}
\caption{%
Hypervisor and VS CSRs added or widened
by the Advanced Interrupt Architecture.
(Parameter HSXLEN is just another name for
SXLEN for hypervisor-extended \mbox{S-mode}).%
}
\label{tab:CSRs-hypervisor}
\end{table*}

@@

CSR \z{vsiselect} is required to support at least a \mbox{9-bit} range
of 0 to \z{0x1FF}, whether or not an IMSIC is implemented.
As with \z{siselect}, values of \z{vsiselect} with the most-significant
bit set (bit $\mbox{XLEN - 1} = \mbox{1}$) are designated for custom
use.
If XLEN changes, the most-significant bit of \z{vsiselect} moves
to the new position, retaining its value from before.

Like \z{siselect} and \z{sireg}, the widths of \z{vsiselect}
and \z{vsireg} are always the current XLEN rather than VSXLEN\@.
Hence, for example, if HSXLEN = 64 and VSXLEN = 32, then these
registers are 64~bits when accessed by a hypervisor in HS-mode
(running RV64 code) but 32~bits for a guest OS in VS-mode (RV32 code).

### 2023-05-09 doc/src/MSLevel.tex
Change widths of *iselect and *ireg CSRs to be always current XLEN
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

The machine-level priorities for major interrupts 0--63 may be
configured by a set of registers accessed through the \z{miselect} and
\z{mireg} CSRs introduced in Chapter~\ref{ch:CSRs}.
When MXLEN =~32, sixteen of these registers are defined, listed below
with their \z{miselect} addresses:
\begin{displayLinesTable}[c@{\quad}l]
\z{0x30} & \z{iprio0} \\
\z{0x31} & \z{iprio1} \\
\dots    & \ \dots \\
\z{0x3F} & \z{iprio15} \\
\end{displayLinesTable}
Each register controls the priorities of four interrupts, with one
\mbox{8-bit} byte per interrupt.
For a number~$k$ in the range 0--15, register \z{iprio}$k$
controls the priorities of interrupts $k\times\mbox{4}$ through
${k\times\mbox{4}+\mbox{3}}$, formatted as follows:
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Priority number for interrupt $k\times\mbox{4}$ \\
bits 15:8  & Priority number for interrupt $k\times\mbox{4}+\mbox{1}$ \\
bits 23:16 & Priority number for interrupt $k\times\mbox{4}+\mbox{2}$ \\
bits 31:24 & Priority number for interrupt $k\times\mbox{4}+\mbox{3}$ \\
\end{displayLinesTable}

When MXLEN =~64, only the even-numbered registers exist:\nopagebreak
\begin{displayLinesTable}[c@{\quad}l]
\z{0x30} & \z{iprio0} \\
\z{0x32} & \z{iprio2} \\
\dots    & \ \dots \\
\z{0x3E} & \z{iprio14} \\
\end{displayLinesTable}
Each register controls the priorities of eight interrupts.
For even~$k$ in the range 0--14, register \z{iprio}$k$
controls the priorities of interrupts $k\times\mbox{4}$ through
${k\times\mbox{4}+\mbox{7}}$, formatted as follows:
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Priority number for interrupt $k\times\mbox{4}$ \\
bits 15:8  & Priority number for interrupt $k\times\mbox{4}+\mbox{1}$ \\
bits 23:16 & Priority number for interrupt $k\times\mbox{4}+\mbox{2}$ \\
bits 31:24 & Priority number for interrupt $k\times\mbox{4}+\mbox{3}$ \\
bits 39:32 & Priority number for interrupt $k\times\mbox{4}+\mbox{4}$ \\
bits 47:40 & Priority number for interrupt $k\times\mbox{4}+\mbox{5}$ \\
bits 55:48 & Priority number for interrupt $k\times\mbox{4}+\mbox{6}$ \\
bits 63:56 & Priority number for interrupt $k\times\mbox{4}+\mbox{7}$ \\
\end{displayLinesTable}

When MXLEN =~64 and \z{miselect} is an odd value in the range
\z{0x31}--\z{0x3F}, attempting to access \z{mireg} raises an illegal
instruction exception.

@@

Supervisor-level priorities for major interrupts 0--63
are optionally configurable
in an array of supervisor-level \z{iprio}$k$ registers accessed through
\z{siselect} and \z{sireg}.
This array has the same structure when SXLEN = 32 or 64 as does the
machine-level \z{iprio} array when MXLEN = 32 or 64, respectively.
To summarize, when SXLEN =~32, there are sixteen \mbox{32-bit}
registers with these \z{siselect} addresses:
\begin{displayLinesTable}[c@{\quad}l]
\z{0x30} & \z{iprio0} \\
\z{0x31} & \z{iprio1} \\
\dots    & \ \dots \\
\z{0x3F} & \z{iprio15} \\
\end{displayLinesTable}
Each register controls the priorities of four interrupts, one
\mbox{8-bit} byte per interrupt.
When SXLEN =~64, only the even-numbered registers exist:
\begin{displayLinesTable}[c@{\quad}l]
\z{0x30} & \z{iprio0} \\
\z{0x32} & \z{iprio2} \\
\dots    & \ \dots \\
\z{0x3E} & \z{iprio14} \\
\end{displayLinesTable}
Each register controls the priorities of eight interrupts.
If SXLEN = 64 and \z{siselect} is an odd value in the range
\z{0x31}--\z{0x3F}, attempting to access \z{sireg} raises an illegal
instruction exception.

>>>>

The machine-level priorities for major interrupts 0--63 may be
configured by a set of registers accessed through the \z{miselect} and
\z{mireg} CSRs introduced in Chapter~\ref{ch:CSRs}.
When XLEN =~32, sixteen of these registers are defined, listed below
with their \z{miselect} addresses:
\begin{displayLinesTable}[c@{\quad}l]
\z{0x30} & \z{iprio0} \\
\z{0x31} & \z{iprio1} \\
\dots    & \ \dots \\
\z{0x3F} & \z{iprio15} \\
\end{displayLinesTable}
Each register controls the priorities of four interrupts, with one
\mbox{8-bit} byte per interrupt.
For a number~$k$ in the range 0--15, register \z{iprio}$k$
controls the priorities of interrupts $k\times\mbox{4}$ through
${k\times\mbox{4}+\mbox{3}}$, formatted as follows:
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Priority number for interrupt $k\times\mbox{4}$ \\
bits 15:8  & Priority number for interrupt $k\times\mbox{4}+\mbox{1}$ \\
bits 23:16 & Priority number for interrupt $k\times\mbox{4}+\mbox{2}$ \\
bits 31:24 & Priority number for interrupt $k\times\mbox{4}+\mbox{3}$ \\
\end{displayLinesTable}

When XLEN =~64, only the even-numbered registers exist:\nopagebreak
\begin{displayLinesTable}[c@{\quad}l]
\z{0x30} & \z{iprio0} \\
\z{0x32} & \z{iprio2} \\
\dots    & \ \dots \\
\z{0x3E} & \z{iprio14} \\
\end{displayLinesTable}
Each register controls the priorities of eight interrupts.
For even~$k$ in the range 0--14, register \z{iprio}$k$
controls the priorities of interrupts $k\times\mbox{4}$ through
${k\times\mbox{4}+\mbox{7}}$, formatted as follows:
\begin{displayLinesTable}[l@{\quad}l]
bits 7:0   & Priority number for interrupt $k\times\mbox{4}$ \\
bits 15:8  & Priority number for interrupt $k\times\mbox{4}+\mbox{1}$ \\
bits 23:16 & Priority number for interrupt $k\times\mbox{4}+\mbox{2}$ \\
bits 31:24 & Priority number for interrupt $k\times\mbox{4}+\mbox{3}$ \\
bits 39:32 & Priority number for interrupt $k\times\mbox{4}+\mbox{4}$ \\
bits 47:40 & Priority number for interrupt $k\times\mbox{4}+\mbox{5}$ \\
bits 55:48 & Priority number for interrupt $k\times\mbox{4}+\mbox{6}$ \\
bits 63:56 & Priority number for interrupt $k\times\mbox{4}+\mbox{7}$ \\
\end{displayLinesTable}

When XLEN =~64 and \z{miselect} is an odd value in the range
\z{0x31}--\z{0x3F}, attempting to access \z{mireg} raises an illegal
instruction exception.

@@

Supervisor-level priorities for major interrupts 0--63
are optionally configurable
in an array of supervisor-level \z{iprio}$k$ registers accessed through
\z{siselect} and \z{sireg}.
This array has the same structure when XLEN = 32 or 64 as does the
machine-level \z{iprio} array.
To summarize, when XLEN =~32, there are sixteen \mbox{32-bit}
registers with these \z{siselect} addresses:
\begin{displayLinesTable}[c@{\quad}l]
\z{0x30} & \z{iprio0} \\
\z{0x31} & \z{iprio1} \\
\dots    & \ \dots \\
\z{0x3F} & \z{iprio15} \\
\end{displayLinesTable}
Each register controls the priorities of four interrupts, one
\mbox{8-bit} byte per interrupt.
When XLEN =~64, only the even-numbered registers exist:
\begin{displayLinesTable}[c@{\quad}l]
\z{0x30} & \z{iprio0} \\
\z{0x32} & \z{iprio2} \\
\dots    & \ \dots \\
\z{0x3E} & \z{iprio14} \\
\end{displayLinesTable}
Each register controls the priorities of eight interrupts.
If XLEN = 64 and \z{siselect} is an odd value in the range
\z{0x31}--\z{0x3F}, attempting to access \z{sireg} raises an illegal
instruction exception.

### 2023-05-09 doc/src/preface.tex
Change widths of *iselect and *ireg CSRs to be always current XLEN
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

>>>>

For alignment with other forthcoming {\RISCV} ISA extensions,
the widths of the indirect-access CSRs, \z{miselect}, \z{mireg},
\z{siselect}, \z{sireg}, \z{vsiselect}, and \z{vsireg}, were
changed to all be the current XLEN rather than being tied to
their respective privilege levels (previously MXLEN for
\z{miselect} and \z{mireg}, SXLEN for \z{siselect} and \z{sireg},
and VSXLEN for \z{vsiselect} and \z{vsireg}).
